Transformations of forecasts for evaluation in an epidemiological context

### 2022-12-01 main.tex

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where y is the true observed value and F the cumulative distribution function (CDF) of predictive distribution. Both the WIS and the CRPS can be understood as a generalisation of the absolute error to predictive distributions. The WIS is itself an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. 
For a single prediction interval, the interval score is computed as the sum of three penalty components, dispersion (width of the prediction interval), underprediction and overprediction,  
%
\begin{linenomath*}
\begin{align*}
 IS_\alpha(F,y) &= (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u) \\
 &= \text{dispersion} + \text{underprediction} + \text{overprediction},    
\end{align*}
\end{linenomath*}
%
where $1()$ is the indicator function, $y$ is the observed value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution, i.e. the lower and upper bound of a single central prediction interval. For a set of $K$ prediction intervals and the median $m$, the WIS is computed as a weighted sum, 
\begin{linenomath*}
\begin{equation*}
\text{WIS} = \frac{1}{K + 0.5} \cdot \left(w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y)\right),    
\end{equation*} 
\end{linenomath*}
where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.

Infectious processes are commonly modelled around the concept of the reproduction number \citep{gosticPracticalConsiderationsMeasuring2020}, the average number of new cases generated by each case in the population.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time~\citep{dushoffSpeedStrengthEpidemic2021}.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellisChallengesControlCOVID192021}.
If case numbers are growing exponentially (for an effective reproduction number greater than 1) and the true modelling task revolves around estimating the reproduction number or the corresponding growth rate, evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number) less than overprediction by the same amount, as errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate.
If one is to assess the ability of forecasts to assess and forecast the underlying infection dynamics, it may be more appropriate to evaluate errors on the growth rate directly.

@@

\subsection{Interpretation as a score based on multiplicative (relative) errors}
\label{sec:methods:relative}

To illustrate the effects of applying the logarithm, let us consider a point forecast $\hat{y}_{t+1}$ for a quantity of interest $y_{t+1}$, such that 
%
\begin{linenomath*}
\begin{equation*}
y_{t+1} = \hat{y}_{t+1} + \varepsilon_{t+1}.
\end{equation*}
\end{linenomath*}
%
The analogue of the WIS / CRPS for point forecasts is the absolute error, and so the score will be determined by the size of the forecast error $\left|\varepsilon_{t+1}\right|$. When taking the logarithm of the forecast and the observation first, then the score is determined by $\left|\varepsilon^*_{t+1}\right|$: 
\begin{linenomath*}
\begin{equation*}
\log y_{t+1} = \log \hat{y}_{t+1} + \varepsilon^*_{t+1}.
\end{equation*}
\end{linenomath*}
%
This corresponds to evaluating a multiplicative error on the original $y_{t+1}$:
%
\begin{linenomath*}
\begin{align*}
\log y_{t+1} &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \Leftrightarrow \\    
y_{t+1} &= \hat{y}_{t+1} \cdot \exp{\varepsilon^*_{t+1}}.    
\end{align*}
\end{linenomath*}
% %>%

On the natural scale, WIS and CRPS increase linearly with increasing absolute distance between forecast and observation (see Figure \ref{fig:change-in-scores}A), regardless of whether the error is large in relative terms. On the log scale, WIS and CRPS conceptually penalise relative errors and increase linearly with an increase in relative errors (see Figure \ref{fig:change-in-scores}D).

The analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: while the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log-transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/SIM-effect-log-score.png}
    \caption{Illustration of the weighted interval score on the natural and the log scale. The WIS
    (black line) is shown for a $\mathcal{N}(1, 0.2)$ predictive distribution (truncated at 0, density represented by the grey area) as a function of the observed value. 
    A: Scores computed on the natural scale (without prior transformation of the predictive distribution and the observed values). The x-axis is shown on a linear scale. C: Scores computed on the logarithmic scale (log-transforming the predictive distribution and the observed values prior to scoring). The x-axis is shown on a linear scale. B, D: Like A, C, but the x-axis is shown on a relative scale.} 
    \label{fig:change-in-scores}
\end{figure}

\section{Interpretation as scoring the exponential growth rate}
\label{sec:methods:growthrate}

Computing a score based on the logarithm of the forecast and the observation is also equivalent to scoring a forecast of the exponential growth rate of the forecast target. The exponential growth rate $r$ governs epidemic growth via (see e.g. \cite{wallingaHowGenerationIntervals2007})
%
\begin{linenomath*}
\begin{equation*}
y_{t + \Delta t} = y_t \cdot \exp(r \cdot \Delta t).
\end{equation*}
\end{linenomath*}
For small $\Delta t$ and $r$ this is approximately equivalent to
\begin{linenomath*}
\begin{equation*}
 y_{t + \Delta t} = y_t \cdot (1 + r \cdot \Delta t),
%y(t) \cdot \exp(r \cdot \Delta t) \approx y(t) \cdot (1 + r \cdot \Delta t),
\end{equation*}
\end{linenomath*}
%
which is sometimes used as an alternative definition ($r$ in this formulation is then called the multiplicative growth rate). Now assume that we predict one step time step ahead, i.e., at time $t$ we predict $y_{t + 1} = \hat{y}_{t + 1} + \varepsilon^*_{t+1}$. Moreover assume that $r$ is time-constant between $t$ and $t + 1$. The score is determined by the size of $\left|\varepsilon^*_{t+1}\right|$, the absolute error of the log-transformed incidence. 
%
\begin{linenomath*}
\begin{align*}
%\varepsilon^*_{t+1} & = \left|\log \hat{y}_{t + 1} - \log y_{t + 1} \right|\\
\varepsilon^*_{t+1} & = \log \hat{y}_{t + 1} - \log y_{t + 1} \\
& = \log \left[\exp(\hat{r}) \cdot y_t\right] - \log \left[\exp(r) \cdot y_t\right] \\
& = \hat{r} - r,
\end{align*}
\end{linenomath*}
where $\hat{r}$ is the predicted exponential growth rate as implied by $\hat{y}(t + 1)$. By log-transforming both the predicted value and the observation prior to applying the absolute error we thus just assess the error in the predicted exponential growth rate. If we apply the same reasoning to an $n$-week-ahead forecast and assume that the growth rate is piece-wise constant with value $r_t$ on $[t, t + 1)$, we get
%
\begin{linenomath*}
\begin{align*}
\epsilon^* & = \log \hat{y}_{t + n} - \log y_{t + n}\\
& = \log\left[\exp\left(\prod_{i = 0}^{n - 1}\hat{r}_{t + i}\right) \cdot y_t\right] - \log\left[\exp\left(\prod_{i = 0}^{n - 1}r_{t + i} \right) \cdot y_t\right]\\
& =   \prod_{i = 0}^{n - 1}\hat{r}_{t + i} \ - \ \prod_{i = 0}^{n - 1}r_{t + i}.
\end{align*}
\end{linenomath*}
We thus evaluate the error in the cumulative growth over the considered $n$-week period.

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on their scores may change through the log-transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.5}{0.9}) = 1.02$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of their prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

@@

>>>>

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the Weighted Interval Score \citep{bracherEvaluatingEpidemicForecasts2021}. 
The CRPS measures the distance of the predictive distribution to the observed data as 
\begin{linenomath*}
\begin{equation*}
    \text{CRPS}(F, y) = \int_{-\infty}^\infty \left( F(x) - 1(x \geq y) \right)^2 dx,
\end{equation*}    
\end{linenomath*}
where $y$ is the true observed value and $F$ the cumulative distribution function (CDF) of predictive distribution. Both the WIS and the CRPS can be understood as a generalisation of the absolute error to predictive distributions. The WIS is itself an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS is commonly defined as 
\begin{linenomath*}
\begin{equation*}
    \text{WIS}(F, y) = \frac{1}{2K + 1} \times \sum_{k = 1}^{2K + 1} \times 2 \left[ 1(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation*}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome, $K$ is the number of central prediction intervals provided, and $m$ is the median forecast.

The dynamics of infectious processes are often described by the complementary concepts of the reproduction number R \citep{gosticPracticalConsiderationsMeasuring2020} and growth rate r \citep{wallingaHowGenerationIntervals2007}, where R describes the strength and r the speed of epidemic growth \citep{dushoffSpeedStrengthEpidemic2021}.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellisChallengesControlCOVID192021}.
If case numbers are growing exponentially and the true modelling task revolves around estimating the reproduction number or the corresponding growth rate, evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number or growth rate) less than overprediction by the same amount, as errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate.
If one is to assess the ability of forecasts to assess and forecast the underlying infection dynamics, it may be more appropriate to evaluate errors on the growth rate directly.

@@

\subsection*{Interpretation as a relative error}
\label{sec:methods:relative}

To illustrate the effect of applying the logarithm prior to evaluating forecasts we consider the absolute error, which the CRPS and WIS generalize to probabilistic forecasts. When considering a point forecast $\hat{y}$ for a quantity of interest $y$, such that 
%
\begin{linenomath*}
\begin{equation*}
y = \hat{y} + \varepsilon,
\end{equation*}
\end{linenomath*}
the absolute error is given by $|\varepsilon|$. When taking the logarithm of the forecast and the observation first (assuming that both are strictly positive), thus considering 
\begin{linenomath*}
\begin{equation*}
\log y = \log \hat{y} + \varepsilon^*,
\end{equation*}
\end{linenomath*}
the resulting absolute error $\left|\varepsilon^*\right|$ can be interpreted as an approximation of various common relative error measures. Using that $\log(a) \approx a - 1$ if $a$ is close to 1, we get
$$
|\varepsilon^*| = |\log \hat{y} - \log y| = \left|\log\left(\frac{\hat{y}}{y}\right) \right| \ \ \stackrel{\text{if } \hat{y} \ \approx \ y}{\approx} \ \ \left| \frac{\hat{y}}{y} - 1 \right| \ \ = \ \ \left| \frac{\hat{y} - y}{y} \right|.
$$
The absolute error after log transformation is thus an approximation of the \textit{absolute percentage error} (APE) \cite{Gneiting2011JASA}. As in the approximation we assumed that $\hat{y} \approx y$, we can just as well interpret it as an approximation of the \textit{relative error} (RE)
$$
\left| \frac{\hat{y} - y}{\hat{y}} \right|
$$
and the \textit{symmetric absolute percentage error} (SAPE)
$$
\left| \ \frac{\hat{y} - y}{y/2 + \hat{y}/2} \ \right|.
$$
As Figure \ref{fig:SAPE} shows, the alignment with the SAPE is in fact the closest and holds quite well even if predicted and observed value differ by a factor of two or three. Moving back to probabilistic forecasts, the CRPS or WIS applied to log-transformed forecasts and outcomes can thus be seen as a probabilistic counterpart to the symmetric absolute percentage error, which offers an appealing intuitive interpretation.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.8\textwidth]{output/figures/SAPE.png}
\caption{Numerical comparison of different measures of relative error/ We consider a prediction of $\hat{y} = 1$ and for different observed values show the  absolute percentage error (APE), relative error (RE), symmetric absolute percentage error (SAPE) and the absolute error applied to log-transformed predictions and observations. $\hat{y}$ denotes the predicted value. A: Error measures as a function of the observed value with the x-axis shown on a linear scale. B: Same, but x-axis shown on a logarithmic scale.}
\label{fig:SAPE}
\end{figure}

%The analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: while the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log-transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

\subsection{Interpretation as scoring the exponential growth rate}
\label{sec:methods:growthrate}

Another interpretation can be based around viewing the process to be forecast as exponential with time-varying growth rate $r(t)$ (see e.g. \cite{wallingaHowGenerationIntervals2007}), i.e.
\begin{linenomath*}
\begin{equation*}
\frac{d}{dt}y(t) = r(t)y(t)
\end{equation*}
\end{linenomath*}
%
which is solved by
%
\begin{linenomath*}
\begin{equation*}
y(t) = y_0 \exp \left( \int_0^t r(t') dt' \right) = y_0 \exp (\bar{r}t)
\end{equation*}
\end{linenomath*}
where $y_0$ is an initial data point and $\bar{r}$ is the mean of the growth rate between the initial time point $0$ and time $t$.

If a forecast $y$ of the time series at time $t$ starts at time 0 with the data point $y_0$ then the absolute error after log transformation at time $t$ is
%
\begin{linenomath*}
\begin{align*}
\epsilon^* &= \left| \log \left[ \hat{y}( t ) \right] - \log \left[ y ( t ) \right] \right|\\
           &= \left| \log \left[ y_0 \exp (\bar{\hat{r}} t ) \right] - \log \left[ y_0 \exp (\bar{r}t) \right] \right|\\
           &= t \left| \bar{\hat{r}} - \bar{r} \right|.
\end{align*}
\end{linenomath*}
%
We thus evaluate the error in the mean exponential growth rate, scaled by the length of the time period considered.

For small $t$ and $\bar{r}$, $ y_0 \exp (\bar{r}t)$ is approximately equivalent to $ y_0 (1 + \bar{r}t)$, which is sometimes used as an alternative definition (r in this second formulation is then called the multiplicative growth rate).

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on their scores may change through the log-transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would be determined  the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.5}{0.9}) = 1.02$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of their prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

@@

\subsection{WIS}
For a single prediction interval, the interval score is computed as the sum of three penalty components, dispersion (width of the prediction interval), underprediction and overprediction,  
%
\begin{linenomath*}
\begin{align*}
 IS_\alpha(F,y) &= (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot 1(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot 1(y \geq u) \\
 &= \text{dispersion} + \text{underprediction} + \text{overprediction},    
\end{align*}
\end{linenomath*}
%
where $1()$ is the indicator function, $y$ is the observed value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution, i.e. the lower and upper bound of a single central prediction interval. For a set of $K$ prediction intervals and the median $m$, the WIS is computed as a weighted sum, 
\begin{linenomath*}
\begin{equation*}
\text{WIS} = \frac{1}{K + 0.5} \cdot \left(w_0 \cdot |y - m| + \sum_{k = 1}^{K} w_k \cdot IS_{\alpha}(F, y)\right),    
\end{equation*} 
\end{linenomath*}
where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.

Computing a score based on the logarithm of the forecast and the observation is also equivalent to scoring a forecast of the exponential growth rate of the forecast target. The exponential growth rate $r$ governs epidemic growth via (see e.g. \cite{wallingaHowGenerationIntervals2007})
%
\begin{linenomath*}
\begin{equation*}
y_{t + \Delta t} = y_t \cdot \exp(r \cdot \Delta t).
\end{equation*}
\end{linenomath*}
For small $\Delta t$ and $r$ this is approximately equivalent to
\begin{linenomath*}
\begin{equation*}
 y_{t + \Delta t} = y_t \cdot (1 + r \cdot \Delta t),
%y(t) \cdot \exp(r \cdot \Delta t) \approx y(t) \cdot (1 + r \cdot \Delta t),
\end{equation*}
\end{linenomath*}
%
which is sometimes used as an alternative definition ($r$ in this formulation is then called the multiplicative growth rate). Now assume that we predict one step time step ahead, i.e., at time $t$ we predict $y_{t + 1} = \hat{y}_{t + 1} + \varepsilon^*_{t+1}$. Moreover assume that $r$ is time-constant between $t$ and $t + 1$. The score is determined by the size of $\left|\varepsilon^*_{t+1}\right|$, the absolute error of the log-transformed incidence. 
%
\begin{linenomath*}
\begin{align*}
%\varepsilon^*_{t+1} & = \left|\log \hat{y}_{t + 1} - \log y_{t + 1} \right|\\
\varepsilon^*_{t+1} & = \log \hat{y}_{t + 1} - \log y_{t + 1} \\
& = \log \left[\exp(\hat{r}) \cdot y_t\right] - \log \left[\exp(r) \cdot y_t\right] \\
& = \hat{r} - r,
\end{align*}
\end{linenomath*}
where $\hat{r}$ is the predicted exponential growth rate as implied by $\hat{y}(t + 1)$. By log-transforming both the predicted value and the observation prior to applying the absolute error we thus just assess the error in the predicted exponential growth rate. If we apply the same reasoning to an $n$-week-ahead forecast and assume that the growth rate is piece-wise constant with value $r_t$ on $[t, t + 1)$, we get
%
\begin{linenomath*}
\begin{align*}
\epsilon^* & = \log \hat{y}_{t + n} - \log y_{t + n}\\
& = \log\left[\exp\left(\sum_{i = 0}^{n - 1}\hat{r}_{t + i}\right) \cdot y_t\right] - \log\left[\exp\left(\sum_{i = 0}^{n - 1}r_{t + i} \right) \cdot y_t\right]\\
& =   \sum_{i = 0}^{n - 1}\hat{r}_{t + i} \ - \ \sum_{i = 0}^{n - 1}r_{t + i}.
\end{align*}
\end{linenomath*}
We thus evaluate the error in the cumulative growth over the considered $n$-week period.
